Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-15 extended_catalog/paper/extended_catalog.tex
more changes

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies to validate this tool
and calculate the LAT's detection threshold to spatially extended
sources.  We then apply this tool to test all sources in the two
year source catalog for extension and report on the discovery
of XXXXXX\todo{What number should be put
here???} new extended sources.
\end{abstract}

@@

The spatial shape of extended soruces can e modeled
as a two dimensional Gaussian
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF for typical sizes look very similar.  Even
though these shapes are significantly different, we demonstrate in
figure~\ref{compare_disk_gauss} that the convolution of shows the
PSF that would be observed for a power-law source of spectral index
2, the probability density function (PDF) for a Gaussian and uniform
disk of width $0.5\deg$, and the convolution of this PDF with the PSF.
The figure shows the convolution for the PSF in the energy range between
1 \gev and 100 \gev and also in the energy range between 10 \gev and
100 \gev.  The convolved shapes do separate better at higher energy, but
nevertheless this plot shows that we are not very sensitive to probing
the exact structure of an extended source.  In this paper we always
assume a uniform disk spatial model.

@@

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{The \gtobssim program is distributed
and supported by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent the types of sources detectable by the LAT.  The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the Pass 7 Version 6 Source instrument
response function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only dept the sources which had a significant point source detection
($\ts>25$).

@@

As an example of why this issue, we describe our test of P72Y3047 for
extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
emission subtracted.  A two year catalog source P72Y3047 was found at the
position $(l,b)=(37.79\deg,1.14\deg)$.  
We find that there appears to be overall some large scale residual in the
diffuse emission along the galactic plane. Furthermore, it appears that
we don't have a great model of the nearby catalog sources. As a result,
P72Y3047 fits to a very large extension of 1.37\deg and the result is
statistically significant with \tsext=51.6.  By looking at the residuals,
it is clear that this complicated region is not well fit even though
the source's extension is statistically significant. For this reason,
we have to perform a series of followup analysis for all of the sources
that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

\section{Test of 1LAC Sources}

@@

Following the LAT's one year catalog, the LAT collaboration published
a list of catalog sources that had a high probability association with
AGN. The first year catalog had 709 AGN associated with 671 distinct
1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
problems with AGN classification, we used only the 599 AGN which made
it into the clean AGN sample.  An AGN association is only considered
clean if it has a high probability of association $P\ge 80\%$, if it is
the only AGN associated with the 1FGL source, and if there are no flags
on the catalog source (\cite{first_cat}). These last two conditions are
especially important for our analysis.  Source confusion may look like
a spatially extended source and flagged catalog sources may correlate
with unmodeled structure in the diffuse emission.

@@

\subsection{2FGL J1627.0-2425c}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be significantly
extended when using photons between 1 \gev and 100 \gev.  The best
fit extension was $0.41\deg\pm0.05\deg$ and the best fit position is
$(l,b)=(353.09\deg, 16.79\deg)$ The source also appeared in the first
fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
was $\tsext=28.9$.  A smoothed counts map showing this source is seen
in figure \ref{1FGL_J1628.6-2419c}.

This source is in a region of remarkably complicated diffuse emission.
Even though it is 16\deg from the Galactic plane,
the source is right on top of the core of the Ophiuchus molecular cloud,
which contains massive star-forming regions that are very bright
in the infrared.  The region has abundant molecular and atomic gas
traced by CO and HI but also plenty of dark gas, the kind that
we find only by its association with dust emission.\todo{Citation Needed}
Embedded star-forming regions make it even more challenging to measure
the column density of dust.\todo{Citation Needed}
\todo[inline]{Note about spectral index being typical of difuse emission}
Although this region is significantly extended, we conclude that what we
are seeing is most likely an inadequacy in the diffuse $\gamma$-ray emission

@@

The two year catalog source 2FGL J1554.4-5317c was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.49\deg\pm 0.04\deg$ and an extension significance of
$\tsext=77.6$ at a position $(l,b)=(328.1387\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a smoothed counts map of this source.

It was found in the one year catalog under the name 1FGL J1554.0-5345c.
To get a good fit of the source, we had to remove the nearby catalog
source 2FGL J1551.3-5333c
which we believed to be suprious. By looking at
the counts map, we saw no differentation in the source at the location
of the two catalog sources. We tested this region for source confusion
by comparing the increase in log likelihood fitting the region as an
extended source (\tsext=77.6) to the increase in log likelihood fitting
the region as two point sources (\tsinc=48.6).  Since the extended
hypothesis is a has a higher likelihood, we conclude that the source is
spatially extended More
information about the dual localization results for this source are
shown in table \ref{dual_localization_results}.

There are no obvious counterparts to this source. Furthermore, this
source is relativly soft with a spectral index 2.31 and
very close to the galacitc plane in a region of large diffuse emission.
We conclude that although this region is significantly extended, it most
likely represents unmodeled diffuse emission.
\todo[inline]{this needs more quantification/description}
\todo[inline]{Improve note about spectral check and lack of hardness}

\subsection{2FGL J0823.0-4246}

@@

The two year catalog source 2FGL J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg$ and an extension
significance of $\tsext=49.2$.  The source was fit to a position of
$(l,b)=(260.31\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
a smoothed counts map of this source.

This soruce is coincident with the one year catalog source named 1FGL J0823.3-4248.
To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254.  We tested the 
region for source confusion by fitting the region instead as two point
sources and obtained $\tsinc=22.2$ which is smaller then \tsext.

\todo[inline]{Describe how this source is Coincident with Puppis A SNR
and give some interpretation of it.}

@@

The two year catalog source 2FGL J1615.2-5138 was found to be
extended using photons with energies between 10 \gev and 100 \gev.
This source is coincident with the one year catalog source named 1FGL
J1613.6-5100c.  We found an extension of $0.52\deg$ with an extension
significance of \tsext=75.3.  The source was fit to a position of
$(l,b)=(331.74\deg,-0.58\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
a smoothed counts map of this source.

 To get a good fit for the region, we had to remove from our
model the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region
we iterativly relocalized the source 2FGL J1615.0-5051 while fitting
the position and extension of 2FGL J1615.2-5138.  We ended up with
a best fit position of the nearby source 2FGL J1615.0-5051 having
moved from $(l,b)=(332.2684,0.043)$ to $(l,b)=(332.365,0.005)$.
In addition,we had to add a new source not in the catalog at the position
of $(l,b)=(332.426,-0.331)$. The moved and now source are shown in
figure~\ref{1FGL_J1613.6-5100c} are shown as the blue and XXXXXXXXXX\todo{what color} crosses
respectivly.  The location of these sources was found by iterativly
fitting the position of these sources as well as the extension of 2FGL
J1615.2-5138 until a stable fit was found.  It is unclear of this new seed
is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
2FGL J1615.0-5051 was not found to be significantly extended using two
years of data but the fit of 2FGL J1615.2-5138 was clearly growing
too large to obsorb residual in the direction of 
J1615.2-5138 until we added the additional point source.

To address the possibility of source confusion, we compared the likelihood 
fitting 2FGL J1615.2-5138 as two point sources to one source.
We found that \tsinc=34.3 which is smaller then \tsext so we believe
that this is extended emission.

@@

\todo[inline]{Describe What this source is/What HESS Source this is near}

@@

The two year catalog source 2FGL J1632.4-4753c was found to be extended
using photons with energies between 10 \gev and 100 \gev.  This source
was found to be consistent with 1FGL J1632.9-4802c.  We fit an
extension of 0.65\deg with an extension significance of \tsext=95.3.
The source was fit to a position of $(l,b)=(336.52\deg,0.06\deg)$.
Figure~\ref{1FGL_J1632.9-4802c}.  shows a smoothed counts map of this
source. The figure shows as a red star the catalog position
of this source.

To get a good fit of the region, had to remove from our model the four
catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
2FGL J1634.4-4743c.4-4820c. These sources all are on top
of this extended source but there is no indication that the emission of
these sources separates.  These sources are indicated as green stars in
figure~\ref{1FGL_J1632.9-4802c}.

In addition we removed from our region the 4 nearby catalog sources 2FGL
J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615, 2FGL J1639.8-4921c
because they were not significant above 10 \gev.  Finally, we had to
relocalized the source 2FGL J1635.4-4717c to a better fit position
$(l,b)=(337.230,0.346)$ and the position of 2FGL J1636.3-4740c to the
better fit position $(l,b)=(336.968,-0.066)$ to get a good overall fit
of our source.

To test for source confusion, we compared the likelihood fitting this
region as one extended source to the likelihood fitting this region as
two point sources. We found $\tsinc=24.8\ll\tsext$ which indicates that
this is extended emission and not source confusion.

\todo[inline]{Describe how ROI was modified.
Note about uncertainty about background sources. 
We model the northwestern source separatly
but not the southeastern 'possible source'.}

\todo[inline]{Describe What this source is/What HESS Source it is near}

@@

Gamma Cygni SNR.

% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% Delete:
% * P72Y3292 - 2FGL J2022.8+3843c
% * P72Y3282 - 2FGL J2019.1+4040
% * P72Y3287 - 2FGL J2020.0+4159
% * P72Y3262 - 2FGL J2013.8+4115c
% * P72Y3260 - 2FGL J2012.4+3955c
% New source
%  * SkyDir(78.854,2.670,SkyDir.GALACTIC)

\todo[inline]{Describe how ROI was modified}

\todo[inline]{
Describe how this source is analyzed more carefully in the paper
\cite{A cocoon of freshly accelerated cosmic rays detected by Fermi
in the Cygnus superbubble}
}

See figure~\ref{1FGL_J2020.0+4049}.

\todo[inline]{explain upcomming publication}

@@

% Delete:
% * P72Y2982 - Not in 2FGL
% * P72Y2979 - 2FGL J1835.5-0649
% * P72Y2993 - 2FGL J1839.0-0539

@@

Near HESS source HESS J1837. Upcomming publication???
\todo[inline]{Describe how ROI was modified}
\todo[inline]{Discuss the upcomming publication}
See figure~\ref{1FGL_J1837.5-0659c}.

@@

\todo[inline]{Describe how ROI was modified}

Vela Jr. Upcomming publication.
\todo[inline]{explain that Vela Jr will be described better in upcomming publication}
See figure~\ref{Vela_Jr}.

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
    \end{center}
    \caption{
    This plot shows that our threshold to detecting the extension of
    a soruce is best for sources with size $~0.5\deg$. It also shows
    that for sources neither very large nor soft, our sensitivity is
    not significantly improved using photons with energy between 100
    \mev and 1 \gev.  The $x$ axis is extension of a simulated uniform
    disk extended source and the $y$ axis is the simulated source's 100
    \mev to 100 \gev photon flux. The curves represent the detection
    threshold to an extended source which is defiend as the flux when
    $\langle\tsext\rangle=25$ for a particular extension.  All sources
    have an assumed power-law spectrum and the different colors are
    for sources of different simulated spectral indices.  The dashed
    line shows simulations using photons with energy between 100 \mev
    and 100 \gev while the solid lien shows simulations using photons
    with energy between 1 \gev and 100 \gev.  The detection threshold
    is for a one year simulation against a Sreekumar-like isotropic
    background.  More information about this plot is presented in
    section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/ic443_counts_slice.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
    \caption{
    The upper plot is the sum of the counts binned in galactic longitudinal
    summed within 2\deg in galactic latitude centered on the SNR
    IC443. The lower plot shows the same image but instead integrated
    in galactic longitude.  Overlaid on the plot is the model predicted
    counts assuming that IC443 is a point source, an extended source,
    and that there is just the diffuse background. These counts slices
    are especially useful for visually assessing the quality of
    the diffuse emission model in the region surrounding an
    extended source candidate.
    \label{counts_slice}
    }
  \end{center}
\end{figure}

>>>>

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies to validate this tool
and calculate the LAT's detection threshold to spatially extended
sources.  We then apply this tool to test all sources in the two
year source catalog for extension and report on the discovery
of XXXXXX\todo{What number should be put
here. Should we report the total number of extended sources instead of the
number of new sources???} new extended sources.
\end{abstract}

@@

The spatial shape of extended sources can e modeled
as a two dimensional Gaussian
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
\end{equation}
Although these shapes are significantly different, the convolution
of them with the PSF for typical sizes look very similar.  Even
though these shapes are significantly different, we demonstrate in
figure~\ref{compare_disk_gauss} that the convolution of shows the
PSF that would be observed for a power-law source of spectral index
2, the probability density function (PDF) for a Gaussian and uniform
disk of width $0.5\deg$, and the convolution of this PDF with the PSF.
The figure shows the convolution for the PSF in the energy range between
1 \gev and 100 \gev and also in the energy range between 10 \gev and
100 \gev.  The convolved shapes do separate better at higher energy, but
nevertheless this plot shows that we are not very sensitive to probing
the exact structure of an extended source.  In this paper we always
assume a uniform disk spatial model.

@@

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent the types of sources detectable by the LAT.  The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the Pass 7 Version 6 Source instrument
response function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only dept the sources which had a significant point source detection
($\ts>25$).

@@

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this issue, we describe our test of 
2FGL J1856.2+0450c for
extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
emission subtracted.  A two year catalog source 
2FGL J1856.2+0450c was found at the
position $(l,b)=(37.79\deg,1.14\deg)$.  
We find that there appears to be overall some large scale residual in the
diffuse emission along the galactic plane. Furthermore, it appears that
we don't have a great model of the nearby catalog sources. As a result,
2FGL J1856.2+0450c fits to a very large extension of 1.37\deg and the result is
statistically significant with \tsext=51.6.  By looking at the residuals,
it is clear that this complicated region is not well fit even though
the source's extension is statistically significant. For this reason,
we have to perform a series of followup analysis for all of the sources
that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

\section{Test of 1LAC Sources}
\label{test_1lac_sources}

@@

Following the LAT's one year catalog, the LAT collaboration published
a list of catalog sources that had a high probability association with
AGN (\cite{first_agn_cat}).
The first year catalog had 709 AGN associated with 671 distinct
1FGL sources at high latitude ($|b|>10\deg$).  To avoid systematic
problems with AGN classification, we used only the 599 AGN which made
it into the clean AGN sample.  An AGN association is only considered
clean if it has a high probability of association $P\ge 80\%$, if it is
the only AGN associated with the 1FGL source, and if there are no flags
on the catalog source (\cite{first_cat}). These last two conditions are
especially important for our analysis.  Source confusion may look like
a spatially extended source and flagged catalog sources may correlate
with unmodeled structure in the diffuse emission.

@@

\subsection{2FGL J1627.0-2425c}
\label{section_ophiuchus}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be
significantly extended when using photons between 1 \gev and 100 \gev.
The best fit extension was $0.53\deg\pm0.06\deg$ and the best fit position
is $(l,b)=(352.87\deg, 16.79\deg)$ The source also appeared in the first
fermi catalog as 1FGL J1628.6-2419c.  and the extension significance
was $\tsext=21.1$.  A counts map showing this source is seen in
figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion, we also
fit this region as two point sources. Since $\tsinc=16.6$ is smaller
than \tsext, the emission is more likeliy to come from an extended source.

This source is in a region of remarkably complicated diffuse emission.
Even though it is 16\deg from the Galactic plane, the source is on top
of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are very bright in the infrared.  We have
overlaid on the plot of figure~\ref{1FGL_J1628.6-2419c} a 100 micrometer
infared image of this region as seen by IRAS and there is good spatial
overlap between with the \gev observed emission
(\cite{iras_rho_ophiuci}).

The region has abundant molecular and atomic gas traced by CO and HI but
also plenty of dark gas, the kind that we find only by its association
with dust emission. Embedded star-forming regions make it even more
challenging to measure the column density of dust.
Although this region is significantly extended, we conclude that what
we are seeing is most likely an inadequacy in the diffuse $\gamma$-ray
emission model.

\todo[inline]{Can we get another citation about dark gas
and stuff?
Better note about spectral index being typical of difuse emission.
Also does this description make sense? Also, is 
citation about IRAS good?}

@@

The two year catalog source 2FGL J1554.4-5317c was found to be extended
using photons with energy between 1 \gev and 100 \gev.  We found an
extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
$\tsext=39.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a counts map of this source.

It was found in the one year catalog under the name 1FGL J1554.0-5345c.
To get a good fit of the source, we had to remove the nearby catalog
source 2FGL J1551.3-5333c which we believed to be suprious. By looking at
the counts map, we saw no differentation in the source at the location
of the two catalog sources. 
These soruce modifications are further described
in the caption to figure~\ref{1FGL_J1554.0-5345c}.

We tested this region for source confusion
by comparing the increase in log likelihood fitting the region as an
extended source to the increase in log likelihood fitting the region
as two point sources. Since $\tsinc=10.2$ is smaller than \tsext, we
conclude that the source is spatially extended and not multiple point
sources. More information about the dual localization results for this
source are shown in table \ref{dual_localization_results}.

There are no obvious counterparts to this source. Furthermore, this
source is relativly soft with a spectral index 2.31 and very close to
the galacitc plane in a region of large diffuse emission.  We conclude
that although this region is significantly extended, it most likely
represents unmodeled diffuse emission.
\todo[inline]{this needs more quantification/description.
Improve the point about how since the source is soft, it
is more consistent with diffuse emission.
}

\subsection{2FGL J0823.0-4246}
\label{section_puppis_a}

@@

The two year catalog source 2FGL J0823.0-4246 was found to be
extended using photons with energy between 1 \gev and 100 \gev.
We found an extension of $0.37\deg\pm0.03\deg$ and an extension
significance of $\tsext=49.2$.  The source was fit to a position of
$(l,b)=(260.32\deg,-3.28\deg)$.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source.

This source is coincident with the one year catalog source named 1FGL
J0823.3-4248.  To get a good fit of the source, we had to remove the
nearby catalog sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which
are part of the extended emission.  We tested the source for spatial
confusion by fitting it as two point sources. Because $\tsinc=22.3$ is
smaller then \tsext, we believe that this source is spatially extended.
These removed catalog soruces are shown in figure~\ref{1FGL_J0823.3-4248}.

This extended source is spatially coincident with the SNR Puppis A.
Overlaid on figure~\ref{1FGL_J0823.3-4248} are ROSAT contours of
Puppis A (\cite{rosat_puppis_a}). There is good agreement
between the measured radius of $\sigma=0.37$ degrees in \gev and 
the X-ray contours of the source.

\todo[inline]{Give some additional interpretation of the Puppis A SNR.}

@@

The two year catalog source 2FGL J1615.2-5138 was found to be extended
using photons with energies between 10 \gev and 100 \gev.  This source
is coincident with the one year catalog source 1FGL J1613.6-5100c.
We found an extension of $0.43\deg\pm0.04\deg$ with an extension
significance of \tsext=45.3.  The source was fit to a position of
$(l,b)=(331.67\deg,-0.66\deg)$.  Figure~\ref{1FGL_J1613.6-5100c} shows
a counts map of this source.

To get a good fit for the region, we had to remove from our model
the nearby catalog sources 2FGL J1520.6-5111c, 2FGL J1619.7-5040c,
and 2FGL J1622.8-5006. Furthermore, to get a good fit of the region we
iterativly relocalized the source 2FGL J1615.0-5051 while fitting the
position and extension of 2FGL J1615.2-5138.  We ended up with a best
fit position of the nearby source 2FGL J1615.0-5051 having moved from
$(l,b)=(332.2684\deg,0.043\deg)$ to $(l,b)=(332.365\deg,0.005\deg)$.  In addition,we
had to add a new source not in the catalog at the position of
$(l,b)=(332.426\deg,-0.331\deg)$.  The location of these sources was found by iterativly
fitting the position of these sources as well as the extension of 2FGL
J1615.2-5138 until a stable fit was found.  It is unclear of this new seed
is physically a new source or if 2FGL J1615.0-5051 is spatially extended.
2FGL J1615.0-5051 was not found to be significantly extended using two
years of data but the fit of 2FGL J1615.2-5138 was clearly growing too
large to obsorb residual in the direction of J1615.2-5138 until we added
the additional point source.
These modifications are further described in the caption to 
figure~\ref{1FGL_J1613.6-5100c}.

To address the possibility of source confusion, we compared the likelihood
fitting 2FGL J1615.2-5138 as two point sources to one source.  We found
that \tsinc=30.1 which is smaller then \tsext so we believe that this
is extended emission.

@@

\todo[inline]{Describe What this source is/What HESS Source this is near}
\todo[inline]{Describe contours overlaied on source}

@@

The two year catalog source 2FGL J1632.4-4753c was found to be extended
using photons with energies between 10 \gev and 100 \gev.  This source
is coincident with the one year catalog source 1FGL J1632.9-4802c.
We fit an extension of $0.44\deg\pm0.04\deg$ with an extension
significance of \tsext=62.2.  The source was fit to a position
of $(l,b)=(336.52\deg,0.06\deg)$.  Figure~\ref{1FGL_J1632.9-4802c}.
shows a counts map of this source.

To get a good fit of the region, we had to remove from our model
the four catalog sources 2FGL J1631.7-4720c, 2FGL J1630.2-4752,
2FGL J1634.4-4743c.4-4820c. These sources all are on top of this
extended source but there is no indication that the emission of these
sources separates.  Finally, we relocalized the
source 2FGL J1635.4-4717c to a better fit position $(l,b)=(337.230\deg,0.346\deg)$
and the position of 2FGL J1636.3-4740c to the better fit position
$(l,b)=(336.968\deg,-0.066\deg)$ to get a good overall fit of our source.
These modifications are further described in the caption to 
figure~\ref{1FGL_J1632.9-4802c}.

In addition we removed from our region four farther away two year
catalog sources J1638.0-4703c, 2FGL J1628.1-4857c, 2FGL  J1630.1-4615,
2FGL J1639.8-4921c because they were not significant above 10 \gev.

To test for source confusion, we compared the likelihood fitting this
region as one extended source to the likelihood fitting this region as
two point sources. We found $\tsinc=38.5\ll\tsext$ which indicates that
this is extended emission and not source confusion.

\todo[inline]{Describe What this source is/What HESS Source it is near}
\todo[inline]{Describe contours overlaid on source}

@@

% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% Delete:
% * P72Y3282 - 2FGL J2019.1+4040
% * P72Y3292 - 2FGL J2022.8+3843c
% * P72Y3287 - 2FGL J2020.0+4159
% * P72Y3262 - 2FGL J2013.8+4115c
% * P72Y3260 - 2FGL J2012.4+3955c
% New source
%  * SkyDir(78.854,2.670,SkyDir.GALACTIC)

The two year catalog source 2FGL J2021.5+4026 was found to be extended
using photons with energies between 10 \gev and 100 \gev. This source
is coincident with the one year catalog source 1FGL J2020.0+4049. We
fit an extension of $0.59\deg\pm0.03\deg$ with an extension
significance of $\tsext=140.6$.  The source was fit to a position of
$(l,b)=(78.17\deg,2.19\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
counts map of this source.

To get a good fit of the region, we had to remove the nearby catalog
source 2FGL J2019.1+4040 which were part of the extended source.
Further, we found it necessary to add an additional point source not in
the two year catalog into our background model.  The new source is was
localized to a position of $(l,b)=(78.854,2.670)$ and had $\ts\approx 16$
(using \pointlike).  Although the source is not very significant, not
including it into the background model appeared visually to significantly
throw off the fit of the region.  In addition, we removed the four
further away catalog sources 2FGL J2022.8+3843c, 2FGL J2020.0+4159,
2FGL J2013.8+4115c, and 2FGL J2012.4+3955c from our region becuase they
were not signifcant above 10\gev.  After modifying the region, we found
that \tsinc=34.7 which is less than \tsext, so we believe that source
source is spatially extended.  These modifications are further described
in the caption to figure~\ref{1FGL_J2020.0+4049}.

\todo[inline]{
This source is the Gamma Cygni SNR!

Describe how this source is analyzed more carefully in the paper
\cite{A cocoon of freshly accelerated cosmic rays detected by Fermi
in the Cygnus superbubble}
}
\todo[inline]{Describe contours overlaid on source}

@@

% Delete:
% * P72Y2982 - Not in 2FGL
% * P72Y2979 - 2FGL J1835.5-0649 - SkyDir(25.0503,0.3894)
% * P72Y2993 - 2FGL J1839.0-0539 - SkyDir(26.4904,0.1632)

@@

The two year catalog source 2FGL J1837.3-0700c was found to be extended
using photons with energies between 10 \gev and 100 \gev. This source
is coincident with the one year catalog source 1FGL J1837.5-0659c. We
fit an extension of $0.35\deg\pm0.08\deg$ with an extension
significance of $\tsext=20.9$.  The source was fit to a position of
$(l,b)=(25.08\deg,0.13\deg)$.  Figure~\ref{1FGL_J2020.0+4049} shows a
counts map of this source.

This source is in a very complicated region. There are two very nearby
catalog sources 2FGL J1836.8-0623c and 2FGL J1837.3-0700c which are
about $~0.5\deg$ away from our source. To get a good fit of the region,
we slightly relocalize these sources so that 2FGL J1836.8-0623c is at
a postiion of $(l,b)=(25.574\deg,0.320\deg)$ and 2FGL J1837.3-0700c is
at a position of $(l,b)=(24.716\deg,0.500\deg)$.  We also relocalized
the source 2FGL J1839.3-0558c which is about $~1\deg$ away from our
source to a better position of $(l,b)=(26.080\deg,0.229\deg)$ Finally,
we had to remove the nearby catalog source 2FGL J1835.5-0649 which we
believed to be part of our extended source. We also removed the farther
away catalog source 2FGL J1839.0-0539 because it was not significant
above 10 \gev.  After modifying the region, we found that \tsinc=15.4
which is less than \tsext, so we believe that the emission from this
soruce spatially extended.  These modifications are further described
in the caption to figure~\ref{1FGL_J2020.0+4049}.

\todo[inline]{
Near HESS source HESS J1837. 
Discuss the upcomming publication???
Describe contours overlaied on source}

@@

The two year catalog source 2FGL J0851.7-4635 was found to be extended
using photons with energies between 10 \gev and 100 \gev. This source has
no counterparts in the first year LAT catalog.  We fit an extension of
$1.12\deg\pm0.07\deg$ with an extension significance of $\tsext=90.9$.
The source was fit to a position of $(l,b)=(266.29\deg,-1.41\deg)$.
Figure~\ref{Vela_Jr} shows a counts map of this source.

To get a good fit of the region, we had to remove three nearby catalog
sources 2FGL J0848.5-4535, 2FGL J0855.4-4625, and 2FGL J0853.5-4711 which
were part of the extended source.  In addition, we had to relocalize
the position of two nearby catalog sources to better fit their position
at high energies.  We localized 2FGL J0854.7-4501 to a position of
$(l,b)=(266.232\deg,0.517\deg)$ and 2FGL J0901.7-4655 to a position of
$(l,b)=(267.311\deg,-0.190\deg)$. In addition, we removed the further
away catalog source 2FGL J0858.0-4815 beacuse it was not significant
above 10 \gev.  After modifying the region, we found that \tsinc=17.2
which is less than \tsext, so we believe that this region is not source
confusion but is instead a spatially extended source.  These modifications
are further described in the caption to figure~\ref{Vela_Jr}.

\todo[inline]{explain that Vela Jr will be described better in upcoming publication}
\todo[inline]{Describe contours overlaid on source}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v9/plot_vs_index.py
    \end{center}
    \caption{
    This plot shows that our threshold to detecting the extension of
    a source is best for sources with size $~0.5\deg$. It also shows
    that for sources neither very large nor soft, our sensitivity is
    not significantly improved using photons with energy between 100
    \mev and 1 \gev.  The $x$ axis is extension of a simulated uniform
    disk extended source and the $y$ axis is the simulated source's 100
    \mev to 100 \gev photon flux. The curves represent the detection
    threshold to an extended source which is defined as the flux when
    $\langle\tsext\rangle=25$ for a particular extension.  All sources
    have an assumed power-law spectrum and the different colors are
    for sources of different simulated spectral indices.  The dashed
    line shows simulations using photons with energy between 100 \mev
    and 100 \gev while the solid lien shows simulations using photons
    with energy between 1 \gev and 100 \gev.  The detection threshold
    is for a one year simulation against a Sreekumar-like isotropic
    background.  More information about this plot is presented in
    section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{ic443_plots/ic443_counts_slice.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/counts_slice_ic443/v1/ic443_counts_slice.pdf
    \caption{ The upper plot is the sum of the counts binned in galactic
    longitudinal summed within 2\deg in galactic latitude centered on the
    SNR IC443. The lower plot shows the same image but instead integrated
    in galactic longitude.  Overlaid on the plot is the model predicted
    counts assuming that IC443 is a point source, an extended source, and
    that there is just the diffuse background.  These plots were generated
    for all extended source candidates.  They are especially useful for
    visually assessing the quality of the diffuse emission model in the
    region surrounding an extended source candidate.} \label{counts_slice}
  \end{center}
\end{figure}
